Carbonate chemistry at Ny-Ålesund

### 2023-03-03 awipev-CO2.Rmd
Changed datetime for Pangaea

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
  dplyr::rename(
    `pressure_profiler [dbar]` = depth,
    # hydrostatic pressure
    `salinity_PSS78_profiler [unit]` = sal_insitu_ctd,
    # salinity in situ
    `salinity_PSS78_ferrybox [unit]` = sal_fb,
    # salinity (FerryBox)
    `temperature_ITS90_11m [°C]` = temp_insitu_11m,
    # temperature in situ (static at 11 m)
    `temperature_ITS90_profiler [°C]` = temp_insitu_ctd,
    # temperature in situ (profiler)
    `temperature_ITS90_ferrybox [°C]` = temp_fb,
    # temperature (FerryBox)
    `temperature_ITS90_seafet_profiler [°C]` = temp_sf,
    # temperature SeaFET (profiler)
    `ta_discrete [umol kg-1]` = at,
    # total alkalinity in situ, discrete measurements
    #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
    `dic_discrete [umol kg-1]` = ct,
    # dissolved inorganic carbon in situ, discrete measurements
    `ph_insitu_temperature_discrete [total scale]` = ph_s_sf_temp_insi,
    # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
    #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
    `pco2_insitu_temperature_ferrybox [uatm]` = pco2_fb_insi_temp,
    # partial pressure of CO2 at in situ temperature (FerryBox)
    #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
    `ph_insitu_temperature_profiler [total scale]` = pHint_tot_sf,
    # pH in situ at in situ temperature (profiler)
    #`pH_dur [total scale]` = pH_dur,
    #`pH_calc [total scale]` = ph_calc_fb
  ) %>% 
  dplyr::mutate(
    across(starts_with("pressure"), ~ round(.x, digits = 2)),
    across(starts_with("salinity"), ~ round(.x, digits = 2)),
    across(starts_with("temperature"), ~ round(.x, digits = 2)),
    across(starts_with("ph"), ~ round(.x, digits = 3)),
    across(
      starts_with("ta") |
        starts_with("dic") |
        starts_with("pco2"),
      ~ round(.x, digits = 1)
    ),
  )
# replace NaNs by NAs
pangaea <- pangaea %>% 
  mutate_all(~ifelse(is.nan(.), NA, .))

>>>>

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
  dplyr::rename(
    `pressure_profiler [dbar]` = depth,
    # hydrostatic pressure
    `salinity_PSS78_profiler [unit]` = sal_insitu_ctd,
    # salinity in situ
    `salinity_PSS78_ferrybox [unit]` = sal_fb,
    # salinity (FerryBox)
    `temperature_ITS90_11m [°C]` = temp_insitu_11m,
    # temperature in situ (static at 11 m)
    `temperature_ITS90_profiler [°C]` = temp_insitu_ctd,
    # temperature in situ (profiler)
    `temperature_ITS90_ferrybox [°C]` = temp_fb,
    # temperature (FerryBox)
    `temperature_ITS90_seafet_profiler [°C]` = temp_sf,
    # temperature SeaFET (profiler)
    `ta_discrete [umol kg-1]` = at,
    # total alkalinity in situ, discrete measurements
    #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
    `dic_discrete [umol kg-1]` = ct,
    # dissolved inorganic carbon in situ, discrete measurements
    `ph_insitu_temperature_discrete [total scale]` = ph_s_sf_temp_insi,
    # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
    #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
    `pco2_insitu_temperature_ferrybox [uatm]` = pco2_fb_insi_temp,
    # partial pressure of CO2 at in situ temperature (FerryBox)
    #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
    `ph_insitu_temperature_profiler [total scale]` = pHint_tot_sf,
    # pH in situ at in situ temperature (profiler)
    #`pH_dur [total scale]` = pH_dur,
    #`pH_calc [total scale]` = ph_calc_fb
  ) %>% 
  dplyr::mutate(
    across(starts_with("pressure"), ~ round(.x, digits = 2)),
    across(starts_with("salinity"), ~ round(.x, digits = 2)),
    across(starts_with("temperature"), ~ round(.x, digits = 2)),
    across(starts_with("ph"), ~ round(.x, digits = 3)),
    across(
      starts_with("ta") |
        starts_with("dic") |
        starts_with("pco2"),
      ~ round(.x, digits = 1)
    ),
  )
# replace NaNs by NAs
pangaea <- pangaea %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) %>% 
  mutate(datetime = as.POSIXct(datetime, origin = "1970-01-01")) |>
  separate(datetime, into = c("Date", "Time"), sep = " ") |>
  mutate(`date/time [UTC+0]` = paste(Date, Time, sep = "T")) |>
  dplyr::select(`date/time [UTC+0]`, everything(), -Date, -Time) |>
  mutate_at(1:13, ~as.character(.)) |>
  mutate_at(1:13, ~replace_na(., ""))
